Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-20 paper-2023-acsos-pulverization.tex
highlight runtime dsk keywords

\lstdefinelanguage{pulv}[]{Kotlin}{
%  basicstyle=\small\ttfamily\lst@ifdisplaystyle\footnotesize\fi,
%	frame=single,
%	escapechar=\%,
%  keywordstyle=\color{blue},
  keywordstyle=[3]\bfseries{},
  keywords=[3]{pulverizedSystem,device,and,deployableOn},
%  sensitive=true,
%  morecomment=[l]{//},
%  morecomment=[n]{/*}{*/},
%  commentstyle=\color{green!40!black},
%  morestring=[b]",
%  morestring=[b]',
%  morestring=[b]""",
%  stringstyle=\ttfamily\color{orange},
}
\lstset{language=pulv,
basewidth=0.555em % decreases spacing between chars
}

@@

\lstinputlisting[
    float=ht,
    language=Kotlin,
    caption={
        Example of the usage of the domain-specific language for the runtime configuration.
        The example defines the runtime configuration of the system, specifying the initial deployment and the reconfiguration rules.
    },
    label=lst:runtime-configuration,
]{listings/RuntimeConfig.kt}

>>>>

\lstdefinelanguage{pulv}[]{Kotlin}{
%  basicstyle=\small\ttfamily\lst@ifdisplaystyle\footnotesize\fi,
%	frame=single,
%	escapechar=\%,
%  keywordstyle=\color{blue},
  keywordstyle=[3]\bfseries{},
  keywords=[3]{pulverizedSystem,device,and,deployableOn,pulverizationRuntime,startsOn,onDevice,reconfigurationRules,reconfigures,movesTo},
%  emph={DeviceBehaviour,DeviceCommunication,DeviceSensors,DeviceActuators,HighLoad,LowBattery},
%  sensitive=true,
%  morecomment=[l]{//},
%  morecomment=[n]{/*}{*/},
%  commentstyle=\color{green!40!black},
%  morestring=[b]",
%  morestring=[b]',
%  morestring=[b]""",
%  stringstyle=\ttfamily\color{orange},
}
\lstset{language=pulv,
basewidth=0.555em % decreases spacing between chars
}

@@

\begin{lstlisting}[
    float=ht,
    language=pulv,
    caption={
        Example of the usage of the domain-specific language for the runtime configuration.
        The example defines the runtime configuration of the system, specifying the initial deployment and the reconfiguration rules.
    },
    label=lst:runtime-configuration,
    numbers=left,
]
// Reconfiguration events
expect fun cpuLoad(): Double
object HighLoad : ReconfigurationEvent<Double>() {
  override val predicate = { it > 0.90 }
  override val events: Flow<Double> = cpuLoad()
}
object LowBattery : ReconfigurationEvent<Double>() {
  override val predicate = { it < 0.20 }
  override val events: Flow<Double> = cpuLoad()
}
// Available hosts
object Smartphone : Host {
  override val hostname = "smartphone"
  override val capabilities = setOf(EmbeddedDevice)
}
object Server : Host {
  override val hostname = "amazon-aws"
  override val capabilities=setOf(HighCPU,LowLatencyComm)
}
// Runtime initial setup and runtime reconfiguration rules
val infrastructure = setOf(Smartphone, Server)
pulverizationRuntime(conf, "iot-sensor", infrastructure) {
  DeviceBehaviour() startsOn Server
  DeviceCommunication() startsOn Server
  DeviceSensors() startsOn Smartphone
  DeviceActuators() startsOn Smartphone
  reconfigurationRules {
    onDevice {
      HighLoad reconfigures {Behaviour movesTo Smartphone}
      LowBattery reconfigures {Behaviour movesTo Server}
    }
  }
}
\end{lstlisting}
